---
title: "Heart Attack Risk Prediction. Final Project"
author: "Giselle Rahimi, Pilar Gore, WonJune Lee, Jiwon Jung, Yoon-hye Cho, Sukyoung Yoon"
date: "`r Sys.Date()`"
---

```{r setup, include = FALSE}
library(tidyverse)
library(dplyr)
library(ggplot2)

untidied_dataset <- read_csv("heart_attack_prediction_dataset.csv")

```

EDA:

```{r}
no_family_history_dataset <- subset(untidied_dataset, `Family History` == 0)
```

```{r}
family_history_dataset <- subset(untidied_dataset, `Family History` == 1)
```

Use summarize on some variables!

Scatterplot with  exercise hours (x axis) , heart attack risk (y axis) Only among people without family history!

```{r}
no_family_history_dataset %>%
  rename(
    `Heart Attack Risk` = "heart_attack_risk"
  )

```

```{r}
no_family_history_dataset %>%
ggplot() +
  geom_boxplot(mapping = aes(x = factor(`Heart Attack Risk`), y = `Exercise Hours Per Week`))+
  labs(title = "PUT TITLE HERE")

```
```{r}
no_family_history_dataset %>%
  group_by(factor(`Heart Attack Risk`)) %>%
    summarize(
    median = median(`Exercise Hours Per Week`)
  )
```

boxplot -> sleep hours (x axis), heart attack risk (y) (without family history) Only among people without family history!

```{r}
```

Histogram -> stress level (x), heart attack risk (y)
```{r}
```

How can we visualize family history with heart attack risk??

```{r}
no_family_history_dataset %>%
  group_by(factor(`Heart Attack Risk`)) %>%
  summarize(n = n())
```
```{r}
family_history_dataset %>%
  group_by(factor(`Heart Attack Risk`)) %>%
  summarize(n = n())
```
Explain the significance of the above numbers!!
```

Tidying:

Remove unwanted columns
change names of columns so they are more neat
separate blood pressure into systolic and diastolic
